Supplement 2

### 2020-09-08 paper/supplement-2.Rmd
edit wording in supplement 2.

This review aimed to estimate the proportion of articles published on
the topic area of football in 2019 that reported on missing data.

@@

Football related articles, published in 2019 were studied. Three major
sports medicine databases were searched using the key terms and limits,
on May 20, 2020. The databases were: SPORTDiscus, Embase and Cinahl. A
list of search terms and complete search statements are provided in
Table \@ref(tab:search-table).

>>>>

This review aimed to estimate the proportion of articles that reported 
missing data in football research.

@@

Football related articles published in 2019 were studied. Three major
sports medicine databases were searched on May 20, 2020, using key terms and limits. 
The databases were: SPORTDiscus, Embase and Cinahl. A
list of the search terms and complete search statements are provided in
Table \@ref(tab:search-table).
